More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
proof in progress second attempt

\item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
\item related works
\end{itemize}
Ludo:
\begin{itemize}
\item[X] reorga sec weak bisim + thm -> 10 Juil
\item[X]  intro et orga globale du papier -> fin aout
\item[NEW] explication dans semantique open pnets et composition
\end{itemize}

@@

Rabea
\begin{itemize}
\item preuve transitivite -> 10 juil
\item proofs of new theorems -> fin juillet
%\item [x] uniformiser p et P pour les pnets 
%\item [x] relectures
\end{itemize}

@@

>>>>

\item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
\end{itemize}
Ludo:
\begin{itemize}
\item[X] reorga sec weak bisim + thm -> 10 Juil
\item  intro et orga globale du papier -> fin aout
\end{itemize}

@@

Rabea
\begin{itemize}
\item preuve transitivite -> 10 juil
\item proofs of new theorems -> fin juillet
%\item [x] uniformiser p et P pour les pnets 
%\item [x] relectures
\end{itemize}
=== en parallele

@@

 --------------------------------

First, using rule (1) we can directly conclude \\

Second by using rule (2),  
\begin{mathpar}
{ \openrule
         {
          \overline{\gamma} \!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar}
implies that 
.\\
Finally by using rule (3) we have
\begin{mathpar}
\inferrule{
\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}{}
\end{mathpar}
and by induction hypothesis this means that we have first,
\begin{mathpar}
%\inferrule{
\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT

implies

\begin{mathpar}
\forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         
\end{mathpar}

such that\\
\begin{mathpar} 
s=s^1_0 \wedge s^1_{n_1}=s_1 \quad
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
\quad
\Pred_1=\bigwedge_{i=0}^{n_1}\Pred^1_i\quad \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1
\end{mathpar}

Secondly,
\begin{mathpar}
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT

\end{mathpar}
implies
\begin{mathpar}
\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\end{mathpar}
such that\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2
\\\\
\overline{\gamma}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}

\end{mathpar}
Finally,
\begin{mathpar}
%\inferrule{
\openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT

implies

\begin{mathpar}
\forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
\end{mathpar}

such that\\
\begin{mathpar} 
s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
\quad
\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
\end{mathpar}

\end{itemize}
\end{proof}

------------------------------------------------------
